Classical Planning Algorithms ¡ on the Atari Video Games

### 2014-11-18 icaps15-paper/paper.tex
Nir iteration over experimental Section

@@

\begin{table*}
\centering
% \addtolength{\tabcolsep}{-2pt}
% {\scriptsize
{\small
\begin{tabular}{@{}l|rr|rr|r|r@{}}
%% table header
% \hline\\[-3ex]
%\hline
\multicolumn{1}{c|}{}& \multicolumn{2}{c|}{$\IW(1)$}& \multicolumn{2}{c|}{\BFS} & \multicolumn{1}{c|}{\BRFS} &  \multicolumn{1}{c}{\UCT}
% \\[.2ex]
\\
% \hline\\\\[-3ex]
\hline
%% table body
\multicolumn{1}{c|}{Game}  &
% \multicolumn{1}{c|}{Avg. Score} &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Avg. Time}\\[.2ex]
 \multicolumn{1}{c}{Score} & \multicolumn{1}{c|}{Time}  &
 \multicolumn{1}{c}{Score} & \multicolumn{1}{c|}{Time}  &
 \multicolumn{1}{c|}{Score} &
 \multicolumn{1}{c}{Score} 
% \\[.2ex]
\\[.2ex]
% \hline\\
\hline

\propername{Assault} & 806.4 & 18.21 & \textbf{852.6} & 25.11 & 413.7 & 1512.2 \\ \hline
\propername{Asterix} & 153400 & 24.33 & 77200 & 26.58 & 2135.7 & \textbf{290700} \\ \hline
\propername{Asteroids} & \textbf{51338} & 65.92 & 22168 & 64.53 & 3127.4 & 4660.6 \\ \hline
\propername{Atlantis} & 159420 & 12.8 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 30460 & \textbf{193858} \\ \hline
\propername{Bank\_heist} & \textbf{717} & 39.29 & 362 & 63.83 & 21.5 & 497.8 \\ \hline
\propername{Battle\_zone} & 11600 & 85.96 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 6312.5 & \textbf{70333.3} \\ \hline
\propername{Beam\_rider} & 9108 & 22.53 & \textbf{9297.6} & 29.03 & 693.5 & 6624.6 \\ \hline
\propername{Berzerk} & \textbf{2096} & 58 & 802 & 73.47 & 195 & 553.5 \\ \hline
\propername{Bowling} & \textbf{68.6} & 9.84 & 50.4 & 59.52 & 25.5 & 25.1 \\ \hline
\propername{Boxing} & 100 & 15.2 & 100 & 22.3 & 100 & 100 \\ \hline
\propername{Breakout} & 384.2 & 4.22 & \textbf{771.6} & 39.47 & 1.1 & 364.4 \\ \hline
\propername{Centipede} & 99207.2 & 39.14 & 93067 & 65.49 & \textbf{125123} & 110422 \\ \hline
\propername{Chopper\_command} & 2100 & 41.06 & 3800 & 40.94 & 1827.3 & \textbf{34018.8} \\ \hline
\propername{Crazy\_climber} & 36160 & 3.61 & 36940 & 58.12 & 37110 & \textbf{98172.2} \\ \hline
\propername{Enduro} & \textbf{500} & 65.69 & 359.4 & 37.66 & 0.6 & 286.3 \\ \hline
\propername{Freeway} & \textbf{30.6} & 31.69 & 22.6 & 60.77 & 0 & 0.4 \\ \hline
\propername{Frostbite} & \textbf{3582} & 12.25 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 137.2 & 270.5 \\ \hline
\propername{Gravitar} & 3920 & 61.85 & \textbf{5980} & 62.45 & 395 & 2850 \\ \hline
\propername{Hero} & \textbf{12887} & 36.63 & 7096.6 & 51.83 & 1323.8 & 12859.5 \\ \hline
\propername{Jamesbond} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \textbf{8550} & 25.68 & 25 & 330 \\ \hline
\propername{Kangaroo} & \textbf{5700} & 7.9 & 5320 & 31 & 90 & 1990 \\ \hline
\propername{Krull} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \textbf{5124} & 36.82 & 3089.2 & 5037 \\ \hline
\propername{Montezuma\_revenge} & 0 & 17.36 & \textbf{80} & 34.72 & 0 & 0 \\ \hline
\propername{Ms\_pacman} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 14781 & 23.97 & 1708.5 & \textbf{22336} \\ \hline
\propername{Pong} & \textbf{21} & 16.67 & \textbf{21} & 34.92 & -20.7 & \textbf{21} \\ \hline
\propername{Pooyan} & 11225 & 7.97 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 909.7 & \textbf{17763.4} \\ \hline
\propername{Qbert} & 3705 & 11.07 & 11680 & 34.61 & 132.8 & \textbf{17343.4} \\ \hline
\propername{Riverraid} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \textbf{5062} & 36.53 & 2178.5 & 4449 \\ \hline
\propername{Seaquest} & \textbf{14272} & 24.91 & 6138 & 33.38 & 288 & 5132.4 \\ \hline
\propername{Space\_invaders} & 2877 & 21.37 & \textbf{3974} & 34.21 & 112.2 & 2718 \\ \hline
\propername{Star\_gunner} & 1540 & 18.89 & \textbf{4660} & 17.62 & 1345 & 1207.1 \\ \hline
\propername{Tennis} & \textbf{23.8} & 21.05 & 23.6 & 36.33 & -23.8 & 2.8 \\ \hline
\propername{Venture} & 775 & 23.41 & \textbf{1080} & 27.78 & 0 & 0 \\ \hline
\propername{Video\_pinball} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 62074.6 & 43.13 & 55567.3 & \textbf{254748} \\ \hline
\propername{Zaxxon} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 15680 & 31.01 & 0 & \textbf{22610} \\ \hline
\multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \hline
Times Best (35 games)& \multicolumn{2}{c|}{12} & \multicolumn{2}{c|}{12} & 1 & 11 \\ \hline
Times Better than UCT (35 games) & \multicolumn{2}{c|}{23} & \multicolumn{2}{c|}{22} & 1  & -- \\ \hline

@@

 \caption{\small Performance that results from random policy and various  lookahead algorithms in 35 Atari games.
The algorithms  are \BRFS, $\IW(1)$, \BFS, and \UCT. Averages  over 5 runs shown with ``random'' seeds
$0$ to $4$, and maximum episode duration of $18,000$  frames. Every algorithm limited to a budget of
150,000 simulated frames, except for UCT limited to 500 rollouts, 300 frames deep instead. Average scores and CPU times per action selection shown.
Performance of UCT taken from \cite{bellemare:jair2013}.
Numbers  in bold show best performer in terms of average score.
--Domains containing (--) are still computing,  each run can take 24 hours of computation. All domains from \cite{bellemare:jair2013}  will be ready for the camera ready--. }
\label{performance}

@@

Interestingly, in terms of average scores out of $35$ games, simple $\IW(1)$ outperforms
\BFS\ and \UCT\ in $18$ and $23$ games respectively,
most often with lower average times per call. \BFS\ outscores \UCT\ in
$22$ of the games \footnote{Note that both \IW\ and \BFS\ may improve, as 6 and 4 games  respectively are not reported in the table
  yet.}. As mentioned in the
previous section, the order in which $\IW(1)$ and \BFS\ generate the
children of an expanded node is randomized, something which has a
potential effect on the novelty measures of nodes, and hence in the
search graph. We found that this randomization helps, in particular in
\Qbert, where not randomizing results in $\IW(1)$ being trapped into
loops sometimes.

>>>>

%Table stuff
\usepackage{xcolor,colortbl}
\definecolor{Gray}{gray}{0.85}
\definecolor{LightCyan}{rgb}{0.88,1,1}

\newcolumntype{a}{>{\columncolor{Gray}}c}
\newcolumntype{b}{>{\columncolor{LightCyan}}c}

\newcommand{\mc}[2]{\multicolumn{#1}{b}{#2}}

@@

\begin{table*}
\centering
% \addtolength{\tabcolsep}{-2pt}
% {\scriptsize
{\small
\begin{tabular}{@{}l|ra|ra|r|r@{}}
%% table header
% \hline\\[-3ex]
%\hline
\multicolumn{1}{c|}{}& \multicolumn{2}{c|}{$\IW(1)$}& \multicolumn{2}{c|}{\BFS} & \multicolumn{1}{c|}{\BRFS} &  \multicolumn{1}{c}{\UCT}
% \\[.2ex]
\\
% \hline\\\\[-3ex]
\hline
%% table body
\multicolumn{1}{c|}{Game}  &
% \multicolumn{1}{c|}{Avg. Score} &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c|}{Avg. Time}  &
% \multicolumn{1}{c}{Avg. Score} & \multicolumn{1}{c}{Avg. Time}\\[.2ex]
 \multicolumn{1}{c}{Score} & \multicolumn{1}{c|}{Time}  &
 \multicolumn{1}{c}{Score} & \multicolumn{1}{c|}{Time}  &
 \multicolumn{1}{c|}{Score} &
 \multicolumn{1}{c}{Score} 
% \\[.2ex]
\\[.2ex]
% \hline\\
\hline

\propername{Assault} & 806.4 & 18.21 & 852.6 & 25.11 & 413.7 & \textbf{1512.2} \\ \hline
\propername{Asterix} & 153400 & 24.33 & 77200 & 26.58 & 2135.7 & \textbf{290700} \\ \hline
\propername{Asteroids} & \mc{1}{\textbf{51338}} & 65.92 & \mc{1}{22168} & 64.53 & 3127.4 & 4660.6 \\ \hline
\propername{Atlantis} & 159420 & 12.8 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 30460 & \textbf{193858} \\ \hline
\propername{Bank\_heist} & \mc{1}{\textbf{717}} & 39.29 & 362 & 63.83 & 21.5 & 497.8 \\ \hline
\propername{Battle\_zone} & 11600 & 85.96 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 6312.5 & \textbf{70333.3} \\ \hline
\propername{Beam\_rider} & \mc{1}{9108} & 22.53 & \mc{1}{\textbf{9297.6}} & 29.03 & 693.5 & 6624.6 \\ \hline
\propername{Berzerk} & \mc{1}{\textbf{2096}} & 58 & \mc{1}{802} & 73.47 & 195 & 553.5 \\ \hline
\propername{Bowling} & \mc{1}{\textbf{68.6}} & 9.84 & \mc{1}{50.4} & 59.52 & 25.5 & 25.1 \\ \hline
\propername{Boxing} & 100 & 15.2 & 100 & 22.3 & 100 & 100 \\ \hline
\propername{Breakout} &\mc{1}{384.2} & 4.22 & \mc{1}{\textbf{771.6}} & 39.47 & 1.1 & 364.4 \\ \hline
\propername{Centipede} & 99207.2 & 39.14 & 93067 & 65.49 & \textbf{125123} & 110422 \\ \hline
\propername{Chopper\_command} & 2100 & 41.06 & 3800 & 40.94 & 1827.3 & \textbf{34018.8} \\ \hline
\propername{Crazy\_climber} & 36160 & 3.61 & 36940 & 58.12 & 37110 & \textbf{98172.2} \\ \hline
\propername{Enduro} & \mc{1}{\textbf{500}} & 65.69 & \mc{1}{359.4} & 37.66 & 0.6 & 286.3 \\ \hline
\propername{Freeway} & \mc{1}{\textbf{30.6}} & 31.69 & \mc{1}{22.6} & 60.77 & 0 & 0.4 \\ \hline
\propername{Frostbite} & \mc{1}{\textbf{3582}} & 12.25 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 137.2 & 270.5 \\ \hline
\propername{Gravitar} & \mc{1}{3920} & 61.85 & \mc{1}{\textbf{5980}} & 62.45 & 395 & 2850 \\ \hline
\propername{Hero} & \mc{1}{\textbf{12887}} & 36.63 & 7096.6 & 51.83 & 1323.8 & 12859.5 \\ \hline
\propername{Jamesbond} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \mc{1}{\textbf{8550}} & 25.68 & 25 & 330 \\ \hline
\propername{Kangaroo} & \mc{1}{\textbf{5700}} & 7.9 & \mc{1}{5320} & 31 & 90 & 1990 \\ \hline
\propername{Krull} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \mc{1}{\textbf{5124}} & 36.82 & 3089.2 & 5037 \\ \hline
\propername{Montezuma\_revenge} & 0 & 17.36 & \mc{1}{\textbf{80}} & 34.72 & 0 & 0 \\ \hline
\propername{Ms\_pacman} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 14781 & 23.97 & 1708.5 & \textbf{22336} \\ \hline
\propername{Pong} & \textbf{21} & 16.67 & \textbf{21} & 34.92 & -20.7 & \textbf{21} \\ \hline
\propername{Pooyan} & 11225 & 7.97 & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 909.7 & \textbf{17763.4} \\ \hline
\propername{Qbert} & 3705 & 11.07 & 11680 & 34.61 & 132.8 & \textbf{17343.4} \\ \hline
\propername{Riverraid} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & \mc{1}{\textbf{5062}} & 36.53 & 2178.5 & 4449 \\ \hline
\propername{Seaquest} & \mc{1}{\textbf{14272}} & 24.91 & \mc{1}{6138} & 33.38 & 288 & 5132.4 \\ \hline
\propername{Space\_invaders} & \mc{1}{2877} & 21.37 & \mc{1}{\textbf{3974}} & 34.21 & 112.2 & 2718 \\ \hline
\propername{Star\_gunner} & \mc{1}{1540} & 18.89 & \mc{1}{\textbf{4660}} & 17.62 & 1345 & 1207.1 \\ \hline
\propername{Tennis} & \mc{1}{\textbf{23.8}} & 21.05 & \mc{1}{23.6} & 36.33 & -23.8 & 2.8 \\ \hline
\propername{Venture} & \mc{1}{775} & 23.41 & \mc{1}{\textbf{1080}} & 27.78 & 0 & 0 \\ \hline
\propername{Video\_pinball} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 62074.6 & 43.13 & 55567.3 & \textbf{254748} \\ \hline
\propername{Zaxxon} & \multicolumn{1}{l}{--} & \multicolumn{1}{l|}{--} & 15680 & 31.01 & 0 & \textbf{22610} \\ \hline
\multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \hline
Times Best (35 games)& \multicolumn{2}{c}{\textbf{12}} & \multicolumn{2}{c}{11} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{\textbf{12}} \\ \hline
Times Better than \IW\ (35 games) & \multicolumn{2}{c}{--} & \multicolumn{2}{c}{\textbf{11}} & \multicolumn{1}{c}{1}  & \multicolumn{1}{c}{9} \\ \hline
Times Better than \BFS\ (35 games) & \multicolumn{2}{c}{\textbf{12}} & \multicolumn{2}{c}{--} & \multicolumn{1}{c}{1}  & \multicolumn{1}{c}{11} \\ \hline
Times Better than \UCT\ (35 games) & \multicolumn{2}{c}{17} & \multicolumn{2}{c}{\textbf{18}} & \multicolumn{1}{c}{1}  & \multicolumn{1}{c}{--} \\ \hline

@@

 \caption{\small Performance that results from random policy and various  lookahead algorithms in 35 Atari games.
The algorithms  are \BRFS, $\IW(1)$, \BFS, and \UCT. Averages  over 5 runs shown with ``random'' seeds
$0$ to $4$, and maximum episode duration of $18,000$  frames. Every algorithm limited to a budget of
150,000 simulated frames, except for UCT limited to 500 rollouts, 300 frames deep instead. Average scores and CPU times per action selection shown.
Performance of UCT taken from \cite{bellemare:jair2013}.
Numbers  in bold show best performer in terms of average score. Numbers with light blue shade show that an algorithm outperformed \UCT.
--Domains containing (--) are still computing,  each run can take 24 hours of computation. All domains from \cite{bellemare:jair2013}  will be ready for the camera ready--. }
\label{performance}

@@

Interestingly, in terms of average scores out of $35$ games, simple $\IW(1)$ outperforms
\BFS\ and \UCT\ in $12$ and $17$ games respectively,
most often with lower average times per call. \BFS\ outscores  \IW\ and \UCT\ in
$11$ and $18$ of the games respectively \footnote{Note that both \IW\ and \BFS\ may improve, as 6 and 4 games  respectively are not reported in the table
  yet.}, and in overall, \IW\ and \UCT\ are the best performer in $12$ games, \BFS\ in $11$ games, and \BRFS in $1$ game. As mentioned in the
previous section, the order in which $\IW(1)$ and \BFS\ generate the
children of an expanded node is randomized, something which has a
potential effect on the novelty measures of nodes, and hence in the
search graph. We found that this randomization helps, in particular in
\Qbert, where not randomizing results in $\IW(1)$ being trapped into
loops sometimes.
